Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
typo

This previous work has focused on the predicted acceptance of \emph{pull requests}. 
By contrast,  we are interested in analyzing the quality 
of a contribution in the context of continuous integration.  While pull requests
quality is determined through manual inspection, continuous integration quality
is automatically determined through test cases, and thus approach the problem of
quality determination differently.
We investigate the factors involved in continuous integration build success.
In this study, we analyze a large set of technical and social attributes 
and how these can be used to predict a contributions quality, measured by the
success of build integration jobs.
We performed this analysis on a large corpus of open source projects
which incorporated continuous integration in their development practice. 
When a contribution to these projects passes integration tests, 
it suggests that the project developers
might have confidence in the changes. 
Thus, we use the commit's build integration status as a proxy for its quality.

@@

\vspace{1ex}
\noindent\textbf{Related work:}
Similar studies have shown the relationship between both social and technical attributes attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} 
show that the social connection between the developer initiating a
pull request and the project integrators is a key factor in predicting 
acceptance of a pull 
request. Unlike this previous study, in our study, we look at a broader aspect of 
social aspects, and focus on predicting the success in Travis
CI jobs. Gousios et al.~\cite{gousios14} found that the change location of a commit was
an important indicator in the acceptance rate of those commits by the project.
Also, the inclusion of test cases with a commit has been shown to increase the
commit's acceptance rate~\cite{gousios15}.
Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. By contrast, we focus on the relationship between independent social 
attributes and continuous integration success.

@@

%\paragraph{External validity} 
Our results might not generalize to 
 other instances outside of the studied cases.  To mitigate this risk, we have used a broad and rich 
 dataset~\cite{msr17challenge} in our analysis, comprising 1,359 popular projects.

 Other concerns of the study include the possibility that the social factors
 have changed significantly in the past three years, the collapsing of a
 commit's build success to a single successful build and unsuccessful build
 distorted the results, and the possibility that unsuccessful builds were due to
 incorrect test cases and not low quality contributions.  Future work will be
 required to investigate the influence of these threats.

>>>>

This previous work has focused on the predicted acceptance of \emph{pull requests}. 
By contrast,  we are interested in analyzing the quality 
of a contribution in the context of continuous integration.  While pull requests
quality is determined through manual inspection, continuous integration quality
is automatically determined through test cases, and thus approach the problem of
quality determination differently.
We investigate the factors involved in continuous integration build success.
In this study, we analyze a large set of technical and social attributes 
and how these can be used to predict a contribution's quality, measured by the
success of build integration jobs.
We performed this analysis on a large corpus of open source projects
which incorporated continuous integration in their development practice. 
When a contribution to these projects passes integration tests, 
it suggests that the project developers
might have confidence in the changes. 
Thus, we use the commit's build integration status as a proxy for its quality.

@@

\vspace{1ex}
\noindent\textbf{Related work:}
Similar studies have shown the relationship between both social and technical attributes attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} 
show that the social connection between the developer initiating a
pull request and the project integrators is a key factor in predicting 
acceptance of a pull 
request. Unlike this previous study, in our study, we look at a broader aspect of 
social aspects, and focus on predicting the success in Travis
CI jobs.Gousios et al.~\cite{gousios14} found that the change location of a commit was
an important indicator in the acceptance rate of those commits by the project.
Also, the inclusion of test cases with a commit has been shown to increase the
commit's acceptance rate~\cite{gousios15}.
Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. By contrast, we focus on the relationship between independent social 
attributes and continuous integration success.

@@

%\paragraph{External validity} 
Our results might not generalize to 
 other instances outside of the studied cases.  To mitigate this risk, we have used a broad and rich 
 dataset~\cite{msr17challenge} in our analysis, comprising 1,359 popular projects.
 Other concerns of the study include the possibility that the social factors
 have changed significantly in the past three years, the collapsing of a
 commit's build success to a single successful build and unsuccessful build
 distorted the results, and the possibility that unsuccessful builds were due to
 incorrect test cases and not low quality contributions.  Future work will be
 required to investigate the influence of these threats.
